Reproducible Research - Peer Assessment 1
=========================================

##Loading and preprocessing the data 
```{r echo=TRUE}
setwd("C:/Users/slussetc/Documents/GitHub/Reproducible_Research/RepData_PeerAssessment1")
activity<-read.csv("activity.csv")
```  
Create a variable for the hours and minutes of day, then create a date time variable to use for plotting.
```{r}
intervaltime<- activity$interval
intervaltime[intervaltime<10]<-paste("0",intervaltime[intervaltime<10],sep="")
intervaltime[intervaltime<100]<-paste("0",intervaltime[intervaltime<100],sep="")
intervaltime[intervaltime<1000]<-paste("0",intervaltime[intervaltime<1000],sep="")
intervaldtime <- strptime(paste(activity$date,intervaltime),format="%Y-%m-%d %H%M")
```  
##What is mean total number of steps taken per day?
Total number of steps taken per day
```{r echo=TRUE}
sum(activity$steps,na.rm=TRUE)
```  
Histogram of Total Steps taken per day
```{r}
hist(activity$steps)
```  

Mean and Median total steps taken per day
```{r}
mean(activity$steps,na.rm=TRUE)
median(activity$steps,na.rm=TRUE)
```  
##What is the average daily activity pattern?
Time Series plot
```{r}
plot(intervaldtime,activity$steps,type="l")
```  

5-minute interval with maximum number of steps
```{r}
intervaldtime[which.max(activity$steps)]
```  
##Imputing Missing Values  
Total number of rows with a missing value
```{r}
sum(rowSums(is.na(activity)))
```  
Missing values will be imputed with the overall mean for the column
```{r}
activity2<-activity
activity2$steps[is.na(activity2$steps)]<-mean(activity2$steps,na.rm=TRUE)
```  
Histogram of newly imputed data
```{r}
hist(activity2$steps)
```  

Mean and Median total number of steps
```{r}
mean(activity2$steps)
median(activity2$steps)
```  
The histogram is only slightly changed.  The mean and the median remain the same.  There are simply no NA's since the overall mean was imputed.

##Are there differences in activity between weekends and weekdays?  
Create a factor variable that is "weekend" or "weekdays"
```{r}
daytype<-weekdays(intervaldtime)
daytype[daytype=='Sunday']<-"Weekend"
daytype[daytype=='Monday']<-"Weekday"
daytype[daytype=='Tuesday']<-"Weekday"
daytype[daytype=='Wednesday']<-"Weekday"
daytype[daytype=='Thursday']<-"Weekday"
daytype[daytype=='Friday']<-"Weekday"
daytype[daytype=='Saturday']<-"Weekend"
library(lattice)
xyplot(activity$steps~activity$interval|daytype,,type="l",layout=c(1,2),
       xlab="Interval",ylab="Number of Steps")
```  


